### 2019-10-30 study.tex
aditya comments addressed

In this section, we present the design of a user study
to evaluate whether 
\noah helps address spreadsheet navigational challenges.
\subsection{Study Design and Participants}
\label{sec:study_design}
\saj{\noah was designed to address the navigational challenges in spreadsheets. As such, the goal of the study was to evaluate whether \noah enhances the navigational capabilities of traditional spreadsheets. Furthermore, we wanted understand how the presence of the features introduced by a plugin like \noah affects a spreadsheet user's navigation experience. In this study, we compare a \noah-integrated spreadsheet with a typical, popular one, Excel, for various navigational tasks in the spreadsheet domain. Similar domain specific evaluations have been performed for measuring the performance of various  overview+detail interfaces, \eg database browsing~\cite{north2000snap} or 
tree navigation~\cite{beard1990navigational}. As explained in Section~\ref{sec:related}, the goals of spreadsheets and the TDA tools are quite different. Therefore, we did not consider TDA tools for the comparative study.}
Our study was designed to answer the following questions:

\squishlist
\item {\bf RQ1.} %\sout{How does the addition of an overview help address spreadsheet navigational challenges, with respect to quantitative performance metrics such as speed and accuracy?}
\saj{How did the addition of an overview like \noah affect a spreadsheet users navigation performance?}
\item {\bf RQ2.} %\sout{How do users make use of the aggregate column results in conjunction with the raw spreadsheet data to analyze data?} 
\saj{How did \noah and it's components impact spreadsheet users'
navigational experiences?}
%\item {\bf RQ3.} \sout{How does bin customization help users inject domain knowledge in addressing their specific exploration questions compared to the automated overview?} \sout{\saj{How do users utilize additional features of \noah, \eg bin customization, during navigation?}
%\item {\bf RQ4.} \sout{How is the user's subjective satisfaction with \noah compared to traditional spreadsheets?}}  \sout{\saj{How is the user's subjective satisfaction with \noah compared to the traditional spreadsheets when performing navigational tasks?}}
\squishend

@@

\begin{table}[!htb]
\scriptsize
 \vspace{-10pt}
\caption{Quiz tasks for the birdstrikes dataset.}
\label{tab:questions}
\centering
\begin{tabular}{l l}
\hline
\multicolumn{1}{c}{Category} & \multicolumn{1}{c}{Question}    \\ \hline
steer                & Organize the data by State. How many flights that \\
                         & had damages (damage = 1) originated from Florida? \\ 
identify     & How many flights in the currently visible \\
                 &  spreadsheet window have damages?                                    \\ 
steer                & How many flights that had damages (damage = 1) \\
                         &   originated from California?                          \\ 
\cmpA & Which state between Florida and California \\
                         &   has a higher number of flights with damages?    \\ 
\cmpB & Find the state with the most birdstrike occurrences.  \\ 
customize       & Organize the data by \emph{altitude}. What is the average \\
                         &   cost of damages for altitude bin 0-450?          \\ \hline
\end{tabular}
\end{table}

@@

\emph{Quiz Tasks.} \saj{We designed six tasks grouped into four categories: 
steer (two tasks), compare (two tasks), identify (one task), and customize (one task), representing the Table~\ref{tab:scope} uses cases \code{summarize}, \code{compare}, \code{identify}, and \code{create}, respectively. All of the tasks except the customize task, are representative of the navigation interactions required for the most frequently issued spreadsheet formulae
~\cite{bradbard2014spreadsheet, lawson2009comparison}. The customize tasks was designed to mimic the scenario where a user would group data subsets of interest and required participants to utilize the bin customization feature. The tasks were presented in the same order as shown in Table~\ref{tab:questions} for the birdstrikes dataset. The questions for the Airbnb dataset were similar. The order of the questions mimics the spreadsheet navigation scenario presented in Section~\ref{sec:usage}.}
%All of these tasks require navigation of the spreadsheet data in the form of either scrolling or steering.

@@

\subsection{Study Limitations.}
\kgk{Our study has several limitations that can be strengthened by future larger-scale and more fine-grained studies. One limitation arises from our participant demographics.  We conducted the study with $20$ participants from four different backgrounds. Our participant pool demographics partially represent the demographics of the general audience intended for \noah.
%is in sample size and participant demographics: we conducted the study with $20$ participants from four different backgrounds.Therefore, our participant pool demographics partially represents the demographics of the general audience intended for \noah.
A larger sample with more participants that better represented the spreadsheet user population would have provided more ecological validity to generalize our findings.
}
%While a larger sample with more diverse backgrounds would have allowed us to perform more definitive quantitative analysis, we combined this analysis with qualitative survey, interview, and screen/audio recording data to provide insights that can be explained with multiple information sources.

\saj{Another limitation of the study is that we only compared the performance of a \noah-integrated spreadsheet with a traditional spreadsheet. We did not evaluate specific spreadsheet features like pivot table and \code{SUBTOTAL} due to their limitations in the types of interactions supported (see Section~\ref{sec:related}). Moreover, we wanted the participants to utilize the typical spreadsheet operations that they are comfortable with to complete those tasks and see how introduction of \noah affected their navigation experience.}

>>>>

In this section, we present the design of a user study
to evaluate whether 
\noah helps address spreadsheet navigational challenges.
\subsection{Study Design and Participants}
\label{sec:study_design}
\newsaj{The goal of our study is to evaluate whether \noah addresses the navigational challenges in traditional spreadsheets. Furthermore, we wanted understand how the presence of the features introduced by a plugin like \noah impacts a spreadsheet user's navigation experience as they explore and make sense of data. Therefore, we decided to compare a \noah-integrated spreadsheet with a typical, popular one, Excel, for various navigational tasks in the spreadsheet domain.} \saj{Similar domain specific-evaluations have been performed for measuring the performance of various  overview+detail interfaces, \eg database browsing~\cite{north2000snap} or 
tree navigation~\cite{beard1990navigational}. As explained in Section~\ref{sec:related}, the goals \newsaj{and user populations} of spreadsheets and TDA tools are quite different. Therefore, we did not consider TDA tools for the comparative study.}
Our study was designed to answer the following questions:
\agp{The RQs feel repetitive. What did Karrie think.}
\newsaj{She was fine with it. I think there are subtle differences. the RQ1 tries corresponds to quantifiable performance metric like accuracy, latency. RQ2 is qualitative feedback of user experience.}
\squishlist
\item {\bf RQ1.} %\sout{How does the addition of an overview help address spreadsheet navigational challenges, with respect to quantitative performance metrics such as speed and accuracy?}
\saj{How did the addition of an overview like \noah impact \newsaj{a user's spreadsheet navigation performance  measured in terms of speed and accuracy?}}
\item {\bf RQ2.} %\sout{How do users make use of the aggregate column results in conjunction with the raw spreadsheet data to analyze data?} 
\saj{How did \noah and it's components affect spreadsheet users'
navigational experiences?}
%\item {\bf RQ3.} \sout{How does bin customization help users inject domain knowledge in addressing their specific exploration questions compared to the automated overview?} \sout{\saj{How do users utilize additional features of \noah, \eg bin customization, during navigation?}
%\item {\bf RQ4.} \sout{How is the user's subjective satisfaction with \noah compared to traditional spreadsheets?}}  \sout{\saj{How is the user's subjective satisfaction with \noah compared to the traditional spreadsheets when performing navigational tasks?}}
\squishend

@@

\begin{table}[!htb]
\scriptsize
 \vspace{-10pt}
\caption{\newsaj{Quiz tasks for the birdstrikes dataset. The use cases correspond to the task typology discussed in Section~\ref{sec:usage}}}
\label{tab:questions}
\centering
\begin{tabular}{l l l}
\hline
Category & Question & Use case    \\ \hline
steer                & Organize the data by State. How many& \\
                     & flights that had damages (damage = 1)& \code{summarize}\\
                     & originated from Florida? \\ 
identify             & How many flights in the currently &\\
                     & visible spreadsheet window  &  \code{identify}\\ 
                     & have damages? & \\
steer                & How many flights that had damages & \code{summarize}\\
                     & originated from California?                         & \\ 
\cmpA                & Which state between Florida and &\\
                     & California  has a higher number of & \code{compare}\\ 
                     & flights with damages?    &\\
\cmpB                & Find the state with the most & \code{compare}\\
                     & birdstrike occurrences.  &\\ 
customize            & Organize the data by \emph{altitude}. &\\
                     & What is the average cost of damages & \code{generate}\\
                     &    for altitude bin 0-450?         & \\ \hline
\end{tabular}
\end{table}

@@

\emph{Quiz Tasks.} \saj{We designed six tasks grouped into four categories: 
steer (two tasks), compare (two tasks), identify (one task), and customize (one task), representing the Table~\ref{tab:scope} uses cases \code{summarize}, \code{compare}, \code{identify}, and \code{generate}, respectively. All of the tasks except the customize task, are representative of the navigation interactions required for the most frequently issued spreadsheet formulae
~\cite{bradbard2014spreadsheet, lawson2009comparison}. The customize tasks was designed to mimic the scenario where a user would group data subsets of interest and required participants to utilize the bin customization feature. The tasks were presented in the same order as shown in Table~\ref{tab:questions} for the birdstrikes dataset. The questions for the Airbnb dataset were similar. The order of the questions mimics the spreadsheet navigation scenario presented in Section~\ref{sec:usage}.}
%All of these tasks require navigation of the spreadsheet data in the form of either scrolling or steering.

@@

\subsection{Study Limitations.}
\saj{Our study has several limitations that can be strengthened by future larger-scale and more fine-grained studies. One limitation arises from our participant demographics.  We conducted the study with $20$ participants from four different backgrounds. Our participant pool demographics partially represent the demographics of the general audience intended for \noah.
%is in sample size and participant demographics: we conducted the study with $20$ participants from four different backgrounds.Therefore, our participant pool demographics partially represents the demographics of the general audience intended for \noah.
A larger sample with more participants that better represented the spreadsheet user population would have provided more ecological validity to generalize our findings.
}
%While a larger sample with more diverse backgrounds would have allowed us to perform more definitive quantitative analysis, we combined this analysis with qualitative survey, interview, and screen/audio recording data to provide insights that can be explained with multiple information sources.

\saj{Another limitation of the study is that we only compared the performance of a \noah-integrated spreadsheet with a traditional spreadsheet. We did not evaluate specific spreadsheet features like pivot table and \code{SUBTOTAL} due to their limitations in the types of interactions supported (see Section~\ref{sec:related}). Moreover, instead of forcing the participants use unfamiliar spreadsheet operations, we wanted them to utilize the typical spreadsheet operations that they are comfortable with, to complete the tasks and see how introduction of \noah affected their navigation experience.}

### 2019-10-30 usecases.tex
aditya comments addressed

\section{\noah Use Cases}
\label{sec:usage}
\new{Users prefer spreadsheets 
over enterprise solutions 
to view, explore, and analyze data~\cite{chan1996use,raden2005shedding}. 
To understand the scope of typical user 
tasks on spreadsheets, 
we make use of the typology 
of abstract data exploration tasks~\cite{brehmer2013multi}---see 
Table~\ref{tab:scope}. 
This typology characterizes the range of domain-independent
tasks performed on visual representations of data,
developed after analyzing task classification 
systems in over two dozen papers, 
and has been applied to a variety of 
scenarios, including XXX\agp{argue for
 utility with citations.}
While all the tasks in Table~\ref{tab:scope} 
can be performed using spreadsheets, 
\noah enhances the experience 
for many of these tasks, 
indicated by a checkmark (\checkmark). 
We describe these tasks in the context
of a real usage scenario for \noah below.
Additional details regarding how \noah 
complements spreadsheets 
in accomplishing these tasks can be found in 
the Appendix.}

>>>>

\section{\noah Use Cases}
\label{sec:usage}
\new{Users prefer spreadsheets 
over enterprise solutions 
to view, explore, and analyze data~\cite{chan1996use,raden2005shedding}. 
To understand the scope of typical user 
tasks on spreadsheets, 
we make use of the typology 
of abstract data exploration tasks~\cite{brehmer2013multi}---see 
Table~\ref{tab:scope}. 
This typology characterizes the range of domain-independent
tasks performed on visual representations of data,
developed after analyzing task classification 
systems in over two dozen papers, 
and can be applied to a variety of 
scenarios, including \newsaj{analytical reasoning during exploration~\cite{shrinivasan2008supporting}, multi-dimensional data analysis~\cite{valiati2006taxonomy}, graph comprehension~\cite{friel2001making}, cartography~\cite{roth2012empirically}, among others.}\agp{argue for
 utility with citations.}
While all the tasks in Table~\ref{tab:scope} 
can be performed using spreadsheets, 
\noah enhances the experience 
for many of these tasks, 
indicated by a checkmark (\checkmark). 
We describe these tasks in the context
of a real usage scenario for \noah below.
Additional details regarding how \noah 
complements spreadsheets 
in accomplishing these tasks can be found in 
the Appendix.}
